---
title: "Belfast_Peacelines"
format: pdf
editor: visual
---

## Belfast Peacelines

Geography students from Newcastle University undertook this project as a omponent of their field trip to Ireland, focusing on the exploration of political concepts and the differences between the "two Irelands".

Following interviews with local residents in Belfast, the group discerned seven distinct peacelines classified into the categories of "formal," "informal," and "invisible."

Using Google Maps, coordinates were obtained and compiled into a CSV file.

```{r}
library(tidyverse)

data <- read_csv("~/Dropbox/Mac/Documents/Newcastle University/fieldtrip/dataset_belfast.csv")

```

Subsequently, the peacelines were graphically represented on the map below:

```{r}
library(leaflet)
library(sf)

sf_data <- st_as_sf(data, coords = c("long", "lat"), crs = 4326)  # Note the order of coordinates

# Plot map with points

map_points <- leaflet(sf_data) %>%
  addTiles() %>%
  addCircleMarkers(
    radius = 5,
    color = ~case_when(
      type == "formal" ~ "blue",
      type == "informal" ~ "green",
      type == "invisible" ~ "red"  # Assigning red color to "invisible"
    ),
    label = ~name,
    popup = ~paste("<br> type: ", type)
  ) %>%
  addLegend("bottomright", colors = c("blue", "green", "red"), 
            labels = c("Formal", "Informal", "Invisible"), title = "Type")

# Display the map
map_points
```

We used the packages "leafleft" and "special features" to plot the points. Each point corresponds to a peaceline location, with colours indicating their respective types: "formal," "informal," and "invisible."
